IFA Comparison of Noncognitive Skills \\ BCS and MCS

### 2018-04-25 codes/R/paper/cohorts_nc.Rnw
commonalities table by gender

\clearpage
\begin{landscape}
\begin{table}[ht]
\centering
\footnotesize
\caption{Item Commonalities}\label{tab:comm}
<<MEANTABLE_RES, dependson="MEANTABLE", results='asis'>>=
require(xtable)

table <- meantab

>>>>

\clearpage
\begin{landscape}
\begin{table}[ht]
\centering
\footnotesize
\caption{Item Commonalities -- Males}\label{tab:comm_m}
<<MEANTABLE_RES_M, dependson="MEANTABLE", results='asis'>>=
require(xtable)

table <- meantab[[1]]

\clearpage
\begin{landscape}
\begin{table}[ht]
\centering
\footnotesize
\caption{Item Commonalities -- Females}\label{tab:comm_f}
<<MEANTABLE_RES_F, dependson="MEANTABLE", results='asis'>>=
require(xtable)

table <- meantab[[2]]
